%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage{hyperref}
\usepackage[utf8]{inputenc}
\usepackage{verbatim}

\hypersetup{
    colorlinks=true,
    linkcolor=black,
    filecolor=black,
    urlcolor=black,
    pdfpagemode=FullScreen,
    }
\urlstyle{same}

\usepackage[left=0.3in,top=0.5in,right=0.4in,bottom=0.5in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{0.3\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{1em}\rlap{#1}}

\name{\bf Julian Awad} % Your name

\address{(613)-806-2681 \\ julian.awad@queensu.ca \\ www.linkedin.com/in/julian-awad}
%\address{\bf{Clearances Held (Canada): NATO Secret \\ Controlled Goods Program \\ Enhanced Reliability}}
\begin{document}

%----------------------------------------------------------------------------------------
%	SUMMARY SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Summary}
Engineering Physics graduate with extensive experience in mechanical engineering, aerospace, and defense. Skilled in designing, analyzing, and testing mechanical systems, including spacecraft components and robotic arms. Proficient in SolidWorks, GD\&T, LabVIEW, and Python, with a strong background in experimental physics and data analysis. Proven ability to improve manufacturability, reliability, and performance through innovative design solutions. Effective communicator and collaborator, experienced in managing cross-functional teams complex projects.
\end{rSection}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Education}

\begin{rSubsection}{Bachelor of Engineering Physics, Mechanical Stream}{September 2019 - May 2024}{}{}{}
  \item Faculty of Engineering at Queen's University, Kingston ON
  \item Dean's List with Honours - GPA of 3.77/4.3
  \item Head of the Brazilian Jiu-Jitsu Club 2020-2024
\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}

\begin{rSubsection}{Rocket Lab (Sinclair Interplanetary)}{January 2023 - August 2023}{Mechanical Engineering Intern}{}
\item Redesigned the entire mechanical assembly of a 1000Nms Reaction Wheel from initial design stages to production leading to significant improvements in manufacturability, ease of assembly, and performance.
\item Collaborated closely with stakeholders, including engineers, technicians, and manufacturers, to gather and integrate their requirements into design decisions; implemented these into CAD models and created detailed engineering drawings using GD\&T principles.
\item Created a test to reliably characterize magnetic fields of different magnetic arrays using Arduino and hall sensors; wrote a test proposal, executed the test, analyzed the data to draw conclusions, and wrote a detailed test report.
\item Assembled, inspected and tested several satellite components currently operating on orbit ensuring consistency, quality, and performance across hundreds of units.
\item Designed and manufactured 7+ Ground Support Equipment to save time and improve workflow in various testing, manufacturing, inspection, and assembly scenarios.
\end{rSubsection}

\begin{rSubsection}{MDA}{May 2022 - December 2022}{Mechanical Engineering Intern}{}
\item Automated the entire end-to-end testing infrastructure for the CANADARM2 using Python, Pandas, and NumPy for efficient parsing, analysis and visualization of test data, leading to 10x time savings.
\item Built a custom NI DAQ system using LabVIEW to be used in several testing scenarios, including up to 20 load cells, 10 LVDTs, and 8 thermocouples.
\item Performed structural testing and analysis for Lunar Gateway Grapple Fixtures and End Effectors to characterize the stiffness of the latched assembly in all directions.
\item Performed end-to-end control systems test campaigns for the CANADARM2 using HITL/SITL simulations.
\end{rSubsection}

\begin{rSubsection}{Lockheed Martin}{May 2021 - August 2021}{Hardware Engineering Intern}{}
\item Performed detailed SolidWorks FEA analysis to validate equipment to Military Standard 901D.
\item Created an Excel VBA tool to generate shock response spectra from an impulse function for shock \& vibe testing, allowing for rapid simulation and validation of equipment to industry standards.
\item Accomplished overall 2x cost reduction and 4x time savings by performing detailed make-vs-buy analysis on electronics enclosures and presenting to senior engineers.
\end{rSubsection}

\begin{comment}
\begin{rSubsection}{Department of National Defense}{May 2020 - August 2020}{Engineering Intern}{}
\item Documented and presented key specifications on armored patrol vehicles for 411 vehicles in 69 variants.
\item Reworked procurement documents based on technical requirements from multiple military bases.
\item Proofread english-to-french translations of contracts to ensure correctness.
\end{rSubsection}
\end{comment}
\pagebreak


\end{rSection}
%----------------------------------------------------------------------------------------
%	TECHNICAL SKILLS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Skills}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} p{4.9in} }
CAD Modelling/Drawing & SolidWorks, Solid Edge, GD\&T, DFM \& DFA, 3D Printing \\
Assembly, Integration \& Test & Test Design, Helicoil Insertion, Quality Inspection, Infor LN \\
Experimental Physics & LabVIEW DAQ, Electronics, Experimental Design, Vacuum Systems \\
Data Analysis & Python, Pandas, Numerical Methods, Scientific Computing, MATLAB \\
Languages &  English \& French (Native Bilingual), Spanish \\
\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
%	PROJECTS AND PUBLICATIONS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Projects \& Publications}

\begin{rSubsection}{Undergraduate Thesis}{September 2023 - April 2024}{Modelling a Relativistic Spacecraft Mission to Detect a Distant Primordial Black Hole Orbiting Our Sun}{}
\item Conducted an 8-month research project on modeling a relativistic spacecraft mission to detect a primordial black hole (PBH) hypothesized to orbit our sun.
\item Synthesized the current literature on the Planet 9 hypothesis and constraints on its location and orbital parameters.
\item Developed a comprehensive model of thermal emissions from accreted matter around the hypothesized Planet 9 PBH, incorporating Bondi's spherical accretion theory.
\item Optimized mission parameters for cost-efficiency and speed using the Breakthrough Starshot initiative framework, aiming to propel spacecraft to relativistic speeds of up to 0.2c.
\item Estimated the number of spacecraft required for a conclusive search for Planet 9 by calculating the effective search radius and subdividing the probable location in the sky.
\item Analyzed the economic feasibility of the mission, including costing for ground stations and per-mission energy costs.
\end{rSubsection}

\begin{rSubsection}{Undergraduate Publication}{September 2021 - December 2021}{An Investigation of Magnetic Radiation Shields for Human Space Habitats}{Awad et al.}
\item Designed and conducted an experiment over 6 weeks to measure the viability of a superconducting magnet as an active shield from radiation, GCRs, and lunar regolith for lightweight space travel applications.
\item Manufactured a vacuum chamber with a cooling tube configuration, wire feed-through, and a beta particle detector capable of maintaining a vacuum of 0.1 Pa to minimize particle stopping power and reduce condensation.
\item Designed superconducting magnet configurations made of superconducting YBCO tape with a vacuum-tight cooling system to maintain critical temperatures of 77K.
\item Created a Python program to perform in-depth analysis of the raw data, including noise filtering, curve fitting, and extrapolation to demonstrate clear trends.
\end{rSubsection}


\begin{rSubsection}{Co-Founder, PolyTwist Designs}{November 2015 - Present}{\url{www.polytwist.xyz}}{}
\item Co-founded a small business designing and manufacturing original Rubik's-Cube-style puzzles with unique mechanisms, challenges, and solutions using FDM 3D Printing and SolidWorks.
\item Designed and manufactured several novel products end-to-end resulting in 16+ original designs.
\item Negotiated a partnership with Rubik's Brand Ltd. to mass-produce a product, involving the design stages to manufacturing through injection molding and packaging design, resulting in over a million units sold internationally
\item Created and maintained a website and online shop resulting in \$20,000 in sales of 16+ products over three years.
\end{rSubsection}

\end{rSection}

\begin{comment}
\begin{rSection}{Relevant Coursework}
\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Experimental Physics & DAQ with LabVIEW, Electronics, 

\end{tabular}
\end{rSection}
\end{comment}

%\begin{comment}
\begin{rSection}{About Me}
\begin{rSubsection}{}{}{}{}{}
\item Certified Advanced Open Water SCUBA diver, have been diving in Mexico and Malaysia so far (ask me for pictures!)
\item Fought Muay Thai, Mixed Martial Arts, and Brazilian Jiu-Jitsu in Thailand for 7 weeks.
\item Can solve a Rubik's Cube in under 20 seconds.
\item Will pet any cat I see, even though I am slightly allergic.
\end{rSubsection}
\end{rSection}
%\end{comment}

\end{document}
